# Getting and Cleaning Data : Course Project
## Created by Sandip Chajjed
## June 16, 2016

## Objective: You should create one R script called run_analysis.R that does the following.
 1 Merges the training and the test sets to create one data set.
 2 Extracts only the measurements on the mean and standard deviation for each measurement.
 3 Uses descriptive activity names to name the activities in the data set
 4 Appropriately labels the data set with descriptive variable names.
 5 From the data set in step 4, creates a second, independent tidy data set with the average 
      of each variable for each activity and each subject. 
    
 One of the most exciting areas in all of data science right now is wearable 
 computing - see for example this article . Companies like Fitbit, Nike, and 
 Jawbone Up are racing to develop the most advanced algorithms to attract new users. 
 The data linked to from the course website represent data collected from the accelerometers
 from the Samsung Galaxy S smartphone. A full description is available at the site where the data was obtained:
 
 
 http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones
 
 Here are the data for the project:
 
 https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
```
The experiments have been carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person performed six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually. The obtained dataset has been randomly partitioned into two sets, where 70% of the volunteers was selected for generating the training data and 30% the test data. 

The sensor signals (accelerometer and gyroscope) were pre-processed by applying noise filters and then sampled in fixed-width sliding windows of 2.56 sec and 50% overlap (128 readings/window). The sensor acceleration signal, which has gravitational and body motion components, was separated using a Butterworth low-pass filter into body acceleration and gravity. The gravitational force is assumed to have only low frequency components, therefore a filter with 0.3 Hz cutoff frequency was used. From each window, a vector of features was obtained by calculating variables from the time and frequency domain.

For each record it is provided:
======================================

- Triaxial acceleration from the accelerometer (total acceleration) and the estimated body acceleration.
- Triaxial Angular velocity from the gyroscope. 
- A 561-feature vector with time and frequency domain variables. 
- Its activity label. 
- An identifier of the subject who carried out the experiment.
```

## Activity label
```
1 WALKING
2 WALKING_UPSTAIRS
3 WALKING_DOWNSTAIRS
4 SITTING
5 STANDING
6 LAYING
```
 
 
 
 
```{r}
library(plyr)
library(dplyr)
```

Attaching package: 'dplyr'

The following objects are masked from 'package:plyr':
 
     arrange, count, desc, failwith, id, mutate, rename, summarise,
     summarize
 The following objects are masked from 'package:stats':
 
     filter, lag
 The following objects are masked from 'package:base':
 
     intersect, setdiff, setequal, union
```{r}
library(data.table)
```
 Attaching package: 'data.table'
 
The following objects are masked from 'package:dplyr':
 
     between, last
     
```{r}
library(tidyr)
```

## Create data folder for this project and put the files in data folder. 
```{r}
if(!file.exists("./data")){dir.create("./data")}
fileurl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(fileurl,destfile="./data/Dataset.zip",method='curl')
```
##Unzip the dataset file
```{r}
unzip(zipfile="./data/Dataset.zip",exdir="./data")
path_DS <- file.path("./data", "UCI HAR Dataset")
files <- list.files(path_DS, recursive= TRUE)
files
```
```
  [1] "activity_labels.txt"                         
  [2] "features_info.txt"                           
  [3] "features.txt"                                
  [4] "README.txt"                                  
  [5] "test/Inertial Signals/body_acc_x_test.txt"   
  [6] "test/Inertial Signals/body_acc_y_test.txt"   
  [7] "test/Inertial Signals/body_acc_z_test.txt"   
  [8] "test/Inertial Signals/body_gyro_x_test.txt"  
  [9] "test/Inertial Signals/body_gyro_y_test.txt"  
 [10] "test/Inertial Signals/body_gyro_z_test.txt"  
 [11] "test/Inertial Signals/total_acc_x_test.txt"  
 [12] "test/Inertial Signals/total_acc_y_test.txt"  
 [13] "test/Inertial Signals/total_acc_z_test.txt"  
 [14] "test/subject_test.txt"                       
 [15] "test/X_test.txt"                             
 [16] "test/y_test.txt"                             
 [17] "train/Inertial Signals/body_acc_x_train.txt" 
 [18] "train/Inertial Signals/body_acc_y_train.txt" 
 [19] "train/Inertial Signals/body_acc_z_train.txt" 
 [20] "train/Inertial Signals/body_gyro_x_train.txt"
 [21] "train/Inertial Signals/body_gyro_y_train.txt"
 [22] "train/Inertial Signals/body_gyro_z_train.txt"
 [23] "train/Inertial Signals/total_acc_x_train.txt"
 [24] "train/Inertial Signals/total_acc_y_train.txt"
 [25] "train/Inertial Signals/total_acc_z_train.txt"
 [26] "train/subject_train.txt"                     
 [27] "train/X_train.txt"                           
 [28] "train/y_train.txt"
```

## Read data from files into the variables 

### Read the Activity files
```{r}
dataActivityTest <- read.table(file.path(path_DS,"test","y_test.txt"),header=FALSE)
dataActivityTrain <- read.table(file.path(path_DS,"train", "y_train.txt"),header=FALSE)
```
### Read the Subject files
```{r}
dataSubjectTest <- read.table(file.path(path_DS,"test","subject_test.txt"), header = FALSE )
dataSubjectTrain <- read.table(file.path(path_DS,"train","subject_train.txt"), header =FALSE)
```

### Read the Features data  files
```{r}
dataFeaturesTest <- read.table(file.path(path_DS,"test","X_test.txt"), header = FALSE)
dataFeaturesTrain <- read.table(file.path(path_DS,"train","X_train.txt"), header = FALSE)
```

## Objective 1: Merge the Training and the Test sets to create one data set
```{r}
dataActivity <- rbind(dataActivityTrain,dataActivityTest)
dataSubject <- rbind(dataSubjectTrain,dataSubjectTest)
dataFeatures <- rbind(dataFeaturesTrain,dataFeaturesTest)

names(dataSubject)<-c("subject")
names(dataActivity)<-c("activity")
dataFeaturesnames <- read.table(file.path(path_DS,"features.txt"), header=FALSE)
names(dataFeatures) <- dataFeaturesnames$V2

dataComb <- cbind(dataSubject,dataActivity)
AllData <- cbind(dataFeatures,dataComb)
```

## Objective 2: Extracts only the measurements on the mean and standard deviation for each measurement.
```{r}
subdataFeaturesNames<-dataFeaturesnames$V2[grep("mean\\(\\)|std\\(\\)", dataFeaturesnames$V2)]
selectedNames<-c(as.character(subdataFeaturesNames), "subject", "activity" )
Data<-subset(AllData,select=selectedNames)
str(Data)
```
```
## 'data.frame':    10299 obs. of  68 variables:
##  $ tBodyAcc-mean()-X          : num  0.289 0.278 0.28 0.279 0.277 ...
##  $ tBodyAcc-mean()-Y          : num  -0.0203 -0.0164 -0.0195 -0.0262 -0.0166 ...
##  $ tBodyAcc-mean()-Z          : num  -0.133 -0.124 -0.113 -0.123 -0.115 ...
##  $ tBodyAcc-std()-X           : num  -0.995 -0.998 -0.995 -0.996 -0.998 ...
##  $ tBodyAcc-std()-Y           : num  -0.983 -0.975 -0.967 -0.983 -0.981 ...
##  $ tBodyAcc-std()-Z           : num  -0.914 -0.96 -0.979 -0.991 -0.99 ...
##  $ tGravityAcc-mean()-X       : num  0.963 0.967 0.967 0.968 0.968 ...
##  $ tGravityAcc-mean()-Y       : num  -0.141 -0.142 -0.142 -0.144 -0.149 ...
##  $ tGravityAcc-mean()-Z       : num  0.1154 0.1094 0.1019 0.0999 0.0945 ...
##  $ tGravityAcc-std()-X        : num  -0.985 -0.997 -1 -0.997 -0.998 ...
##  $ tGravityAcc-std()-Y        : num  -0.982 -0.989 -0.993 -0.981 -0.988 ...
##  $ tGravityAcc-std()-Z        : num  -0.878 -0.932 -0.993 -0.978 -0.979 ...
##  $ tBodyAccJerk-mean()-X      : num  0.078 0.074 0.0736 0.0773 0.0734 ...
##  $ tBodyAccJerk-mean()-Y      : num  0.005 0.00577 0.0031 0.02006 0.01912 ...
##  $ tBodyAccJerk-mean()-Z      : num  -0.06783 0.02938 -0.00905 -0.00986 0.01678 ...
##  $ tBodyAccJerk-std()-X       : num  -0.994 -0.996 -0.991 -0.993 -0.996 ...
##  $ tBodyAccJerk-std()-Y       : num  -0.988 -0.981 -0.981 -0.988 -0.988 ...
##  $ tBodyAccJerk-std()-Z       : num  -0.994 -0.992 -0.99 -0.993 -0.992 ...
##  $ tBodyGyro-mean()-X         : num  -0.0061 -0.0161 -0.0317 -0.0434 -0.034 ...
##  $ tBodyGyro-mean()-Y         : num  -0.0314 -0.0839 -0.1023 -0.0914 -0.0747 ...
##  $ tBodyGyro-mean()-Z         : num  0.1077 0.1006 0.0961 0.0855 0.0774 ...
##  $ tBodyGyro-std()-X          : num  -0.985 -0.983 -0.976 -0.991 -0.985 ...
##  $ tBodyGyro-std()-Y          : num  -0.977 -0.989 -0.994 -0.992 -0.992 ...
##  $ tBodyGyro-std()-Z          : num  -0.992 -0.989 -0.986 -0.988 -0.987 ...
##  $ tBodyGyroJerk-mean()-X     : num  -0.0992 -0.1105 -0.1085 -0.0912 -0.0908 ...
##  $ tBodyGyroJerk-mean()-Y     : num  -0.0555 -0.0448 -0.0424 -0.0363 -0.0376 ...
##  $ tBodyGyroJerk-mean()-Z     : num  -0.062 -0.0592 -0.0558 -0.0605 -0.0583 ...
##  $ tBodyGyroJerk-std()-X      : num  -0.992 -0.99 -0.988 -0.991 -0.991 ...
##  $ tBodyGyroJerk-std()-Y      : num  -0.993 -0.997 -0.996 -0.997 -0.996 ...
##  $ tBodyGyroJerk-std()-Z      : num  -0.992 -0.994 -0.992 -0.993 -0.995 ...
##  $ tBodyAccMag-mean()         : num  -0.959 -0.979 -0.984 -0.987 -0.993 ...
##  $ tBodyAccMag-std()          : num  -0.951 -0.976 -0.988 -0.986 -0.991 ...
##  $ tGravityAccMag-mean()      : num  -0.959 -0.979 -0.984 -0.987 -0.993 ...
##  $ tGravityAccMag-std()       : num  -0.951 -0.976 -0.988 -0.986 -0.991 ...
##  $ tBodyAccJerkMag-mean()     : num  -0.993 -0.991 -0.989 -0.993 -0.993 ...
##  $ tBodyAccJerkMag-std()      : num  -0.994 -0.992 -0.99 -0.993 -0.996 ...
##  $ tBodyGyroMag-mean()        : num  -0.969 -0.981 -0.976 -0.982 -0.985 ...
##  $ tBodyGyroMag-std()         : num  -0.964 -0.984 -0.986 -0.987 -0.989 ...
##  $ tBodyGyroJerkMag-mean()    : num  -0.994 -0.995 -0.993 -0.996 -0.996 ...
##  $ tBodyGyroJerkMag-std()     : num  -0.991 -0.996 -0.995 -0.995 -0.995 ...
##  $ fBodyAcc-mean()-X          : num  -0.995 -0.997 -0.994 -0.995 -0.997 ...
##  $ fBodyAcc-mean()-Y          : num  -0.983 -0.977 -0.973 -0.984 -0.982 ...
##  $ fBodyAcc-mean()-Z          : num  -0.939 -0.974 -0.983 -0.991 -0.988 ...
##  $ fBodyAcc-std()-X           : num  -0.995 -0.999 -0.996 -0.996 -0.999 ...
##  $ fBodyAcc-std()-Y           : num  -0.983 -0.975 -0.966 -0.983 -0.98 ...
##  $ fBodyAcc-std()-Z           : num  -0.906 -0.955 -0.977 -0.99 -0.992 ...
##  $ fBodyAccJerk-mean()-X      : num  -0.992 -0.995 -0.991 -0.994 -0.996 ...
##  $ fBodyAccJerk-mean()-Y      : num  -0.987 -0.981 -0.982 -0.989 -0.989 ...
##  $ fBodyAccJerk-mean()-Z      : num  -0.99 -0.99 -0.988 -0.991 -0.991 ...
##  $ fBodyAccJerk-std()-X       : num  -0.996 -0.997 -0.991 -0.991 -0.997 ...
##  $ fBodyAccJerk-std()-Y       : num  -0.991 -0.982 -0.981 -0.987 -0.989 ...
##  $ fBodyAccJerk-std()-Z       : num  -0.997 -0.993 -0.99 -0.994 -0.993 ...
##  $ fBodyGyro-mean()-X         : num  -0.987 -0.977 -0.975 -0.987 -0.982 ...
##  $ fBodyGyro-mean()-Y         : num  -0.982 -0.993 -0.994 -0.994 -0.993 ...
##  $ fBodyGyro-mean()-Z         : num  -0.99 -0.99 -0.987 -0.987 -0.989 ...
##  $ fBodyGyro-std()-X          : num  -0.985 -0.985 -0.977 -0.993 -0.986 ...
##  $ fBodyGyro-std()-Y          : num  -0.974 -0.987 -0.993 -0.992 -0.992 ...
##  $ fBodyGyro-std()-Z          : num  -0.994 -0.99 -0.987 -0.989 -0.988 ...
##  $ fBodyAccMag-mean()         : num  -0.952 -0.981 -0.988 -0.988 -0.994 ...
##  $ fBodyAccMag-std()          : num  -0.956 -0.976 -0.989 -0.987 -0.99 ...
##  $ fBodyBodyAccJerkMag-mean() : num  -0.994 -0.99 -0.989 -0.993 -0.996 ...
##  $ fBodyBodyAccJerkMag-std()  : num  -0.994 -0.992 -0.991 -0.992 -0.994 ...
##  $ fBodyBodyGyroMag-mean()    : num  -0.98 -0.988 -0.989 -0.989 -0.991 ...
##  $ fBodyBodyGyroMag-std()     : num  -0.961 -0.983 -0.986 -0.988 -0.989 ...
##  $ fBodyBodyGyroJerkMag-mean(): num  -0.992 -0.996 -0.995 -0.995 -0.995 ...
##  $ fBodyBodyGyroJerkMag-std() : num  -0.991 -0.996 -0.995 -0.995 -0.995 ...
##  $ subject                    : int  1 1 1 1 1 1 1 1 1 1 ...
##  $ activity                   : int  5 5 5 5 5 5 5 5 5 5 ...
```
## Objective 3: Uses descriptive activity names to name the activities in the data set
```{r}
activityLabels <- read.table(file.path(path_DS,"activity_labels.txt"),header =FALSE)
Data$activity <-as.character(Data$activity)
for ( i in 1:6){
    Data$activity[Data$activity==i]<-as.character(activityLabels[i,2])
}

Data$activity <- as.factor(Data$activity)
head(Data$activity,30)
```

```
##  [1] STANDING STANDING STANDING STANDING STANDING STANDING STANDING
##  [8] STANDING STANDING STANDING STANDING STANDING STANDING STANDING
## [15] STANDING STANDING STANDING STANDING STANDING STANDING STANDING
## [22] STANDING STANDING STANDING STANDING STANDING STANDING SITTING 
## [29] SITTING  SITTING 
## 6 Levels: LAYING SITTING STANDING WALKING ... WALKING_UPSTAIRS
```
## Objective 4: Appropriately labels the data set with descriptive variable names.
```{r}
names(Data) <- gsub("^t","time",names(Data))
names(Data) <- gsub("^f","frequency",names(Data))
names(Data) <-gsub("Acc","Accelerometer",names(Data))
names(Data) <-gsub("Gyro","Gyroscope",names(Data))
names(Data) <-gsub("Mag","Magnitude",names(Data))
names(Data) <-gsub("BodyBody","Body",names(Data))
head(names(Data),30)
```
```
##  [1] "timeBodyAccelerometer-mean()-X"    
##  [2] "timeBodyAccelerometer-mean()-Y"    
##  [3] "timeBodyAccelerometer-mean()-Z"    
##  [4] "timeBodyAccelerometer-std()-X"     
##  [5] "timeBodyAccelerometer-std()-Y"     
##  [6] "timeBodyAccelerometer-std()-Z"     
##  [7] "timeGravityAccelerometer-mean()-X" 
##  [8] "timeGravityAccelerometer-mean()-Y" 
##  [9] "timeGravityAccelerometer-mean()-Z" 
## [10] "timeGravityAccelerometer-std()-X"  
## [11] "timeGravityAccelerometer-std()-Y"  
## [12] "timeGravityAccelerometer-std()-Z"  
## [13] "timeBodyAccelerometerJerk-mean()-X"
## [14] "timeBodyAccelerometerJerk-mean()-Y"
## [15] "timeBodyAccelerometerJerk-mean()-Z"
## [16] "timeBodyAccelerometerJerk-std()-X" 
## [17] "timeBodyAccelerometerJerk-std()-Y" 
## [18] "timeBodyAccelerometerJerk-std()-Z" 
## [19] "timeBodyGyroscope-mean()-X"        
## [20] "timeBodyGyroscope-mean()-Y"        
## [21] "timeBodyGyroscope-mean()-Z"        
## [22] "timeBodyGyroscope-std()-X"         
## [23] "timeBodyGyroscope-std()-Y"         
## [24] "timeBodyGyroscope-std()-Z"         
## [25] "timeBodyGyroscopeJerk-mean()-X"    
## [26] "timeBodyGyroscopeJerk-mean()-Y"    
## [27] "timeBodyGyroscopeJerk-mean()-Z"    
## [28] "timeBodyGyroscopeJerk-std()-X"     
## [29] "timeBodyGyroscopeJerk-std()-Y"     
## [30] "timeBodyGyroscopeJerk-std()-Z"
```

## Objective 5: From the data set in step 4, creates a second, independent tidy data set 
## with the average of each variable for each activity and each subject.

```{r}
Data2 <- aggregate(. ~subject + activity,Data, mean)
Data2 <- Data2[order(Data2$subject,Data2$activity),]
write.table(Data2, file="tidydata.txt",row.name=FALSE)
head(Data2,3)
```

```
##    subject activity timeBodyAccelerometer-mean()-X
## 1        1   LAYING                      0.2215982
## 31       1  SITTING                      0.2612376
## 61       1 STANDING                      0.2789176
##    timeBodyAccelerometer-mean()-Y timeBodyAccelerometer-mean()-Z
## 1                    -0.040513953                     -0.1132036
## 31                   -0.001308288                     -0.1045442
## 61                   -0.016137590                     -0.1106018
##    timeBodyAccelerometer-std()-X timeBodyAccelerometer-std()-Y
## 1                     -0.9280565                    -0.8368274
## 31                    -0.9772290                    -0.9226186
## 61                    -0.9957599                    -0.9731901
##    timeBodyAccelerometer-std()-Z timeGravityAccelerometer-mean()-X
## 1                     -0.8260614                        -0.2488818
## 31                    -0.9395863                         0.8315099
## 61                    -0.9797759                         0.9429520
##    timeGravityAccelerometer-mean()-Y timeGravityAccelerometer-mean()-Z
## 1                          0.7055498                        0.44581772
## 31                         0.2044116                        0.33204370
## 61                        -0.2729838                        0.01349058
##    timeGravityAccelerometer-std()-X timeGravityAccelerometer-std()-Y
## 1                        -0.8968300                       -0.9077200
## 31                       -0.9684571                       -0.9355171
## 61                       -0.9937630                       -0.9812260
##    timeGravityAccelerometer-std()-Z timeBodyAccelerometerJerk-mean()-X
## 1                        -0.8523663                         0.08108653
## 31                       -0.9490409                         0.07748252
## 61                       -0.9763241                         0.07537665
##    timeBodyAccelerometerJerk-mean()-Y timeBodyAccelerometerJerk-mean()-Z
## 1                        0.0038382040                        0.010834236
## 31                      -0.0006191028                       -0.003367792
## 61                       0.0079757309                       -0.003685250
##    timeBodyAccelerometerJerk-std()-X timeBodyAccelerometerJerk-std()-Y
## 1                         -0.9584821                        -0.9241493
## 31                        -0.9864307                        -0.9813720
## 61                        -0.9946045                        -0.9856487
##    timeBodyAccelerometerJerk-std()-Z timeBodyGyroscope-mean()-X
## 1                         -0.9548551                -0.01655309
## 31                        -0.9879108                -0.04535006
## 61                        -0.9922512                -0.02398773
##    timeBodyGyroscope-mean()-Y timeBodyGyroscope-mean()-Z
## 1                 -0.06448612                 0.14868944
## 31                -0.09192415                 0.06293138
## 61                -0.05939722                 0.07480075
##    timeBodyGyroscope-std()-X timeBodyGyroscope-std()-Y
## 1                 -0.8735439                -0.9510904
## 31                -0.9772113                -0.9664739
## 61                -0.9871919                -0.9877344
##    timeBodyGyroscope-std()-Z timeBodyGyroscopeJerk-mean()-X
## 1                 -0.9082847                    -0.10727095
## 31                -0.9414259                    -0.09367938
## 61                -0.9806456                    -0.09960921
##    timeBodyGyroscopeJerk-mean()-Y timeBodyGyroscopeJerk-mean()-Z
## 1                     -0.04151729                    -0.07405012
## 31                    -0.04021181                    -0.04670263
## 61                    -0.04406279                    -0.04895055
##    timeBodyGyroscopeJerk-std()-X timeBodyGyroscopeJerk-std()-Y
## 1                     -0.9186085                    -0.9679072
## 31                    -0.9917316                    -0.9895181
## 61                    -0.9929451                    -0.9951379
##    timeBodyGyroscopeJerk-std()-Z timeBodyAccelerometerMagnitude-mean()
## 1                     -0.9577902                            -0.8419292
## 31                    -0.9879358                            -0.9485368
## 61                    -0.9921085                            -0.9842782
##    timeBodyAccelerometerMagnitude-std()
## 1                            -0.7951449
## 31                           -0.9270784
## 61                           -0.9819429
##    timeGravityAccelerometerMagnitude-mean()
## 1                                -0.8419292
## 31                               -0.9485368
## 61                               -0.9842782
##    timeGravityAccelerometerMagnitude-std()
## 1                               -0.7951449
## 31                              -0.9270784
## 61                              -0.9819429
##    timeBodyAccelerometerJerkMagnitude-mean()
## 1                                 -0.9543963
## 31                                -0.9873642
## 61                                -0.9923678
##    timeBodyAccelerometerJerkMagnitude-std()
## 1                                -0.9282456
## 31                               -0.9841200
## 61                               -0.9930962
##    timeBodyGyroscopeMagnitude-mean() timeBodyGyroscopeMagnitude-std()
## 1                         -0.8747595                       -0.8190102
## 31                        -0.9308925                       -0.9345318
## 61                        -0.9764938                       -0.9786900
##    timeBodyGyroscopeJerkMagnitude-mean()
## 1                             -0.9634610
## 31                            -0.9919763
## 61                            -0.9949668
##    timeBodyGyroscopeJerkMagnitude-std()
## 1                            -0.9358410
## 31                           -0.9883087
## 61                           -0.9947332
##    frequencyBodyAccelerometer-mean()-X frequencyBodyAccelerometer-mean()-Y
## 1                           -0.9390991                          -0.8670652
## 31                          -0.9796412                          -0.9440846
## 61                          -0.9952499                          -0.9770708
##    frequencyBodyAccelerometer-mean()-Z frequencyBodyAccelerometer-std()-X
## 1                           -0.8826669                         -0.9244374
## 31                          -0.9591849                         -0.9764123
## 61                          -0.9852971                         -0.9960283
##    frequencyBodyAccelerometer-std()-Y frequencyBodyAccelerometer-std()-Z
## 1                          -0.8336256                         -0.8128916
## 31                         -0.9172750                         -0.9344696
## 61                         -0.9722931                         -0.9779373
##    frequencyBodyAccelerometerJerk-mean()-X
## 1                               -0.9570739
## 31                              -0.9865970
## 61                              -0.9946308
##    frequencyBodyAccelerometerJerk-mean()-Y
## 1                               -0.9224626
## 31                              -0.9815795
## 61                              -0.9854187
##    frequencyBodyAccelerometerJerk-mean()-Z
## 1                               -0.9480609
## 31                              -0.9860531
## 61                              -0.9907522
##    frequencyBodyAccelerometerJerk-std()-X
## 1                              -0.9641607
## 31                             -0.9874930
## 61                             -0.9950738
##    frequencyBodyAccelerometerJerk-std()-Y
## 1                              -0.9322179
## 31                             -0.9825139
## 61                             -0.9870182
##    frequencyBodyAccelerometerJerk-std()-Z frequencyBodyGyroscope-mean()-X
## 1                              -0.9605870                      -0.8502492
## 31                             -0.9883392                      -0.9761615
## 61                             -0.9923498                      -0.9863868
##    frequencyBodyGyroscope-mean()-Y frequencyBodyGyroscope-mean()-Z
## 1                       -0.9521915                      -0.9093027
## 31                      -0.9758386                      -0.9513155
## 61                      -0.9889845                      -0.9807731
##    frequencyBodyGyroscope-std()-X frequencyBodyGyroscope-std()-Y
## 1                      -0.8822965                     -0.9512320
## 31                     -0.9779042                     -0.9623450
## 61                     -0.9874971                     -0.9871077
##    frequencyBodyGyroscope-std()-Z
## 1                      -0.9165825
## 31                     -0.9439178
## 61                     -0.9823453
##    frequencyBodyAccelerometerMagnitude-mean()
## 1                                  -0.8617676
## 31                                 -0.9477829
## 61                                 -0.9853564
##    frequencyBodyAccelerometerMagnitude-std()
## 1                                 -0.7983009
## 31                                -0.9284448
## 61                                -0.9823138
##    frequencyBodyAccelerometerJerkMagnitude-mean()
## 1                                      -0.9333004
## 31                                     -0.9852621
## 61                                     -0.9925425
##    frequencyBodyAccelerometerJerkMagnitude-std()
## 1                                     -0.9218040
## 31                                    -0.9816062
## 61                                    -0.9925360
##    frequencyBodyGyroscopeMagnitude-mean()
## 1                              -0.8621902
## 31                             -0.9584356
## 61                             -0.9846176
##    frequencyBodyGyroscopeMagnitude-std()
## 1                             -0.8243194
## 31                            -0.9321984
## 61                            -0.9784661
##    frequencyBodyGyroscopeJerkMagnitude-mean()
## 1                                  -0.9423669
## 31                                 -0.9897975
## 61                                 -0.9948154
##    frequencyBodyGyroscopeJerkMagnitude-std()
## 1                                 -0.9326607
## 31                                -0.9870496
## 61                                -0.9946711
```
